%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV Hugo Bollon - Single page optimized version
% Template: https://www.overleaf.com/latex/templates/awesome-cv/dfnvtnhzhhbm

\documentclass[11pt, a4paper]{awesome-cv}

% Configuration ------------------------------------------------
\geometry{left=1.2cm, top=1.0cm, right=1.2cm, bottom=1.2cm, footskip=.5cm}  % Reduced margins
\colorlet{awesome}{awesome-red}  % Choose theme color
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}  % Separator
\renewcommand{\acvSectionTopSkip}{4pt}
\renewcommand{\acvSectionContentTopSkip}{2mm}


% Personal Data -------------------------------------------------
\name{Hugo}{Bollon}
\position{Backend / DevOps Engineer \& Open Source Enthusiast}
\address{Grenoble, France}
\mobile{(+33) 6 51 99 80 78}
\email{hugo.bollon@proton.me}
\homepage{hugobollon.me}
\github{hbollon}
\linkedin{hugobollon}
\extrainfo{Driving license: B}

% Begin Document -----------------------------------------------
\begin{document}

%-------------------- Profile ----------------------------------
\makecvheader

\cvsection{Summary}

\cvparagraph{
Passionate software engineer specialized in \textbf{Go} and \textbf{Open Source}, with solid experience in \textbf{backend development} and \textbf{DevOps engineering} (Kubernetes, AWS, CI/CD). After several years designing and maintaining cloud platforms, I now wish to put my skills and motivation to work on high-impact projects as a \textbf{Backend or Fullstack engineer}.
}

%-------------------- Skills -----------------------------------
\cvsection{Skills}

\begin{cvskills}
  \cvskill
    {Languages}
    {Go, Python, Java, C/C++, JavaScript, TypeScript, Bash}
  \cvskill
    {Frontend}
    {Vue, Angular}
  \cvskill
    {Backend}
    {API REST, Gorm, Gin, Echo, Gorilla Mux}
  \cvskill
    {DevOps}
    {Kubernetes, Docker, Helm, ArgoCD, Pulumi, Terraform, GitOps, AWS (EKS, RDS, EC2, ECS, Fargate), IaC, CI/CD}
  \cvskill
    {Database}
    {PostgreSQL, SQLite, Neo4j}
  \cvskill
    {Environments}
    {Linux, Git, GitHub Actions, GitLab CI}
  \cvskill
    {Languages}
    {French (native level), English B2 (TOEIC 905), Japanese A1 (learning)}
\end{cvskills}

%-------------------- Experience -------------------------------
\cvsection{Experience}

\begin{cventries}
  \cventry
    {DevOps Engineer}
    {Camptocamp SA}
    {Chambéry, France}
    {Sep. 2021 - Present}
    {
      \vspace{2.0mm}
      \begin{cvitems}
        \item {Design, automation, and maintenance of Kubernetes clusters with multiples cloud providers (AWS, Exoscale, Scaleway) using Infrastructure as Code (Pulumi, Terraform) for reliable and scalable platforms.}
        \item {Backend development in Go for internal tools, APIs, and automations. External open-source contributions (Terraform providers, Zitadel, etc.).}
        \item {Open-source lead for the Infrastructure department: management, maintenance, and evolution of Camptocamp Infrastructure Solutions' publicly licensed projects.}
        \item {Design and management of CI pipelines to automate build, lint, test, and release stages, using Github Actions and Dagger.}
        \item {Implementation of CD pipelines based on GitOps practices with ArgoCD, ensuring automated, reproducible, and secure Kubernetes deployments.}
        \item {Containerization and orchestration of workloads: Docker image design, Docker Compose configuration, orchestrated deployments with Kubernetes, and containerized CI with Dagger.}
        \item {Close collaboration with the Geospatial department: development of scripts and tools in Python and JavaScript (Vue 3, Angular), design of Helm charts, and optimization of Docker images for packaging and deploying their applications.}
        \item {Deployment and configuration of Monitoring, Logging, and Alerting solutions (Prometheus, Elastic, Grafana).}
        \item {Federated OIDC authentication via Keycloak and Zitadel.}
      \end{cvitems}
    }

  \cventry
    {Go Developer Intern}
    {Camptocamp SA}
    {Chambéry, France}
    {Jun. 2021 - Sep. 2021}
    {
      \vspace{2.0mm}
      \begin{cvitems}
        \item {Development and maintenance of Terraboard (Terraform observability tool).}
        \item {Migration of the frontend from AngularJS to Vue 3 / TypeScript.}
        \item {Backend API development in Go (Gorm, Gorilla Mux).}
        \item {Writing unit tests and CI/CD automation.}
      \end{cvitems}
    }

  \cventry
    {Android Developer Intern}
    {LAET - ENTPE}
    {Chambéry, France}
    {Jan. 2020 - May 2020}
    {
      \vspace{2.0mm}
      \begin{cvitems}
        \item {Native Android app (Java) for digitizing the Urbalog board game with multi-device support using Nearby Connections API.}
      \end{cvitems}
    }

\end{cventries}

%-------------------- Education --------------------------------
\cvsection{Education}

\begin{cventries}
  \cventry
    {MSc Computer Science (with honours)}
    {University Savoie Mont-Blanc}
    {Le-Bourget-Du-Lac, France}
    {2020 -- 2022}
    {}

  \cventry
    {BSc Computer Science (with honours)}
    {University Savoie Mont-Blanc}
    {Le-Bourget-Du-Lac, France}
    {2017 -- 2020}
    {}

  \cventry
    {Scientific Baccalaureate (ISN)}
    {High School of l'Albanais}
    {Rumilly, France}
    {2014 -- 2017}
    {}

\end{cventries}

%-------------------- Certifications ---------------------------
\cvsection{Certifications}

\begin{itemize}
  \item {\textbf{TOEIC}: 905/990 (Feb 2022) — Listening: 440/495 (B2), Reading: 465/495 (C1)}
  \item {\textbf{AWS Certified Cloud Practitioner} (June 2023) — ID: PST3Q8DCVE41Q5GD}
\end{itemize}

%-------------------- Strengths --------------------------------
\cvsection{Strengths}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc}
Takes initiative & Self-taught & Sociable & Attentive to requirements & Fast learner & Team spirit \\
\end{tabular*}

\end{document}
